Selective electroporation of the viral envelope

### 2021-04-19 documents/lessons_learned.tex
rk4 integrator
PSOPT constants calculation
good lord it's done

@@

Why do problems keep happening? Why do bugs which other people have hit keep recurring? Why does bad science even happen?

>>>>

Made a bonehead mistake while installing lanl-ansi fork of Ipopt. While screwing around in the very beginning, I had accidentally added to -L to the LDFLAGS environment variable. This completely broke the installation. I spent almost 4 hours trying to figure that out. I suppose having a list of commands would perhaps improve things...

LLIS

write in the highest-level language first , then translate.

@@

Why do problems keep happening? Why do bugs which other people have hit keep recurring? Why does bad science even happen?
laser power supply troubles paper
